### 2024-06-02 player-evaluation.qmd
20240601 - empirical question

>>>>

The discussion that follows is based on my and others' *impressions* of which characteristics may be valuable to consider when evaluating players.
However, the extent to which any factor is actually relevant for predicting future performance is an empirical question and should be evaluated empirically.
